An Open-Source Implementation of the CMPS Algorithm for Assessing  Similarity of Bullets

### 2021-06-08 CMPSpaper_writing/CMPSpaper_writing.Rmd
couple of edits

        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: finding top five peaks in the original scale, double the segment length and recalculate the cross-correlation function, then identify 3 peaks in the second scale and repeat the process for a basis segment that is doubled again to identify 1 peak in the third scale. \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.

@@

The `CMPS` package contains a simple example to illustrate the basic usage of the package. The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].  The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above). 
The two bullets under consideration here are known to have been fired from the same gun barrel, so for the 36 land-by-land comparisons, 6 comparison are from same-source pairs (known matches) while 30 are from different-source pairs (known non-matches). To access the example data, we use

@@

`bullets$sigs` is a list of 12 numeric vectors corresponding to 12 bullet signatures as shown in \autoref{fig:sigs}. `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].

@@

*   The first element is a plot called `segment_shift_plot`, which is shown in \autoref{fig:sigplot}. On this plot only the congruent matching profile segments are plotted along with the comparison signature at the congruent registration position.

@@

*   The second element is a plot called `signature_shift_plot`, which is shown in \autoref{fig:sigplot2}. On this visual both the reference signature and the comparison signature are plotted. The reference signature is aligned with the comparison signature based on the congruent registration position. And the congruent matching profile segments are highlighted with solid lines.

@@

As `cmps_signature_plot()` focuses on the signature level, on the other hand, `cmps_segment_plot()` focuses on the segment level. It not only takes the "full result" of `extract_feature_cmps()`, but also takes an argument `seg.idx`, indicating which segment to be inspected. As shown in \autoref{fig:segplots}, for example, after checking `sig.plot$seg_shift` we noticed that segment 6 is not one of the congruent matching profile segments. So we can set `seg.idx = 6` in order to take a closer look at segment 6 and understand the reason why it disagrees with the congruent registration position. `cmps_segment_plot()` also returns a list, of which each element corresponds to one segment scale of this basis segment. Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.

>>>>

        -   If `npeaks.set` is an integer vector of length more than 1, for example `npeaks.set = c(5, 3, 1)`, the multi-segment lengths strategy will be used: find the top five peaks \hh{at the first level}, double the segment length and recalculate the cross-correlation function, then identify 3 peaks \hh{at the second level} and repeat the process for a basis segment that is doubled again to identify 1 peak at the third level. \autoref{fig:seg_all} shows an example of 3 scales of basis segment 6 and their corresponding cross-correlation curves and identified peaks.

@@

The `CMPS` package contains a simple example to illustrate the basic usage of the package. The data in this example are twelve bullet signatures obtained from two bullets in Hamby set 252 [@hamby].  The procedure for generating signatures from high-resolution 3D topographic scans of bullet lands used here follows the methodology described in @aoas (as discussed above). 
The two bullets under consideration are known to have been fired from the same gun barrel, so for the 36 pairwise land-by-land comparisons, six comparison are from same-source pairs (known matches) while thirty are from different-source pairs (known non-matches). To access the example data, we use

@@

`bullets$sigs` is a list of twelve numeric vectors corresponding to the twelve bullet signatures shown in \autoref{fig:sigs}. `bullets$source` contains the URLs to the corresponding x3p file containing the topographic scan  from the NIST Ballistics Toolmark Research Database [@nistdb].

@@

*   The first element is a plot called `segment_shift_plot`, shown in \autoref{fig:sigplot}. On this plot the reference signature is drawn as a black line,  congruent matching profile segments from the comparison signature are overlaid in red at the congruent registration position.

@@

*   The second plot is called `signature_shift_plot`, shown in \autoref{fig:sigplot2}. This visual presents both the reference signature and the comparison signature. The comparison signature is aligned with the reference signature based on the congruent registration position. Congruent matching profile segments are highlighted by  solid red lines.

@@

While `cmps_signature_plot()` focuses on the signature level,  `cmps_segment_plot()` focuses on the segment level. It provides the "full result" of `extract_feature_cmps()`, but also takes an argument, `seg.idx`, indicating which segment should be inspected.  When checking `sig.plot$seg_shift` we notice that  segment number 6 is not one of the congruent matching profile segments. We can therefore set `seg.idx = 6` in `cmps_segment_plot()` and investigate the reason why this segment disagrees with the congruent registration position.
\autoref{fig:segplots}  shows the top five registration positions for segment number 6 overlaid on top of the reference signature using hashed lines, the solid line in black shows the original position of the segment (which in this instance is close to the actual registration position). 
Then at each segment scale, we will have two plots, `segment_plot` and `scale_ccf_plot`.
